Computer Science House Constitution

### 2024-03-03 constitution.tex
resolve #37 - VOTING AMENDMENT 🎉 (#135)
:yippee: :party-kirby: :dancing_penguin:

\asubsection{Non-Semantic Changes}
There are two methods for non-semantic change to the Constitution.
A Maintainer may approve any proposed change that does not affect the meaning of the document.
Alternatively, the change may be presented to the House for discussion followed by an Immediate Vote.
A quorum of fifty percent of the Total Number of Possible Votes is required for passage.

\asubsection{Semantic Changes}
Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in the House during the week.
The final proposal is presented the following week and ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}.
The ballots are collected for a minimum of a forty-eight hour period.
A quorum of two-thirds of the Total Number of Possible Votes must cast ballots for the vote to be official.
A vote equaling or exceeding two-thirds of the number of votes cast is required for the change to be placed into the constitution.
The Constitution may be overridden by an immediate House vote as described in \ref{Immediate Vote}.
There must be a quorum of eighty-five percent of the Total Number of Possible Votes for the vote to be official.
A vote equaling or exceeding ninety percent of the number of votes cast is required for the override to take effect.

@@

\asubsection{Maintainer Expectations}
Maintainers are expected to:
\begin{itemize}
	\item Be knowledgeable about the Constitution
	\item Review changes to the Constitution for grammar, spelling, and internal consistency
	\item Participate in discussion of proposals and amendments
	\item Keep a public record of changes to the Constitution
\end{itemize}
Failure to meet any of these expectations is grounds for revocation of Maintainer status by E-Board.

\asubsection{Maintainer Term}
Maintainer status lasts until it is resigned, or until it is revoked by Executive Board vote.
A Maintainer may resign at any time by notifying the current Executive Board and Maintainer group.

If a Maintainer no longer satisfies \ref{Maintainer Qualifications}, they lose Maintainer status.

\asubsection{Maintainer Selection}
Any member may nominate a qualified member for Maintainer status to E-Board for consideration.
E-Board may choose to approve or reject the nomination by Simple Majority vote.

@@

\asubsection{Active Membership Selection}
Qualifying members may self-select into Active Membership by paying dues to the Financial Director and notifying the Evals Director.
\\*\\*
Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evals Director of their intent to participate, who will bring them up for a Simple Majority vote at the next House meeting.
If the vote passes the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.

@@

\asubsection{Active Membership Privileges}
Active Members receive the privilege to:
\begin{itemize}
	\item Vote on all issues brought before the House
	\item Reside on the House
	\item Hold an E-Board office on the House
	\item Use Computer Science House facilities
	\item Attend Computer Science House functions
	\item Receive priority for available housing on the House when returning from cooperative education
	\item Guaranteed housing in compliance with ResLife policies regarding Special Interest Houses and the Housing Selection Process (if they have On-Floor status)
\end{itemize}
Active Members currently on co-op forfeit their right to vote on house issues, and likewise do not count towards quorum.
Exceptions may be made at the discretion of the Evals Director.

@@

\asection{Honorary and Advisory Memberships}
\asubsection{Honorary Membership Qualifications}
Honorary Membership is open to a person whom the House feels has contributed great personal effort to the House and is deserving of House recognition.
\asubsection{Advisory Membership Qualifications}
Advisory Membership is open to all members of the RIT professional, academic, or administrative staff.
\asubsection{Honorary and Advisory Membership Selection}
\begin{enumerate}
	\item A House Member submits to the Evals Director a nomination, in writing, for a person they feel is deserving of Honorary or Advisory Membership. The nomination must specify the type of membership the nominee is nominated for.
	\item The Evals Director performs preliminary research on the candidate and presents the findings.
	\item E-Board decides whether or not to present the nomination to the House for a secret ballot House vote.
		If E-Board decides not to present the nomination to the House, the Selection Process ends and the candidate does not become a Member.
	\item The nomination is presented at a House Meeting for discussion and a Two-Thirds vote, as defined in \ref{Two-Thirds}.
		Ballots are distributed and voting must remain open for a minimum of forty-eight hour period.
	\item Candidates selected for Honorary Membership are notified of their selection as an Honorary Member and presented with the honor.
    \item Candidates selected for Advisory Membership are notified of their acceptance as House Advisors and asked to accept or decline
        the selection.
\end{enumerate}
\asubsection{Honorary Membership Expectations}
Honorary Members are encouraged to remain in contact with the House.
\asubsection{Advisory Membership Expectations}
Advisors are encouraged to offer advice and assistance to the House in any capacity the Advisor is able to help.
Advisors are also encouraged to meet House members and occasionally attend House activities.
\asubsection{Honorary and Advisory Membership Privileges}
Honorary and Advisory Members may advise in all issues brought before the House, use Computer Science House facilities, and attend Computer Science House functions.
\asubsection{Honorary and Advisory Membership Evaluations}
Honorary and Advisory Members are not subject to formal evaluations.
\asubsection{Honorary and Advisory Membership Resignations}
An Honorary or Advisory Member may resign by submitting in writing the reason for resignation to the Chair.
The resignation will be read at the following House Meeting and become effective at that time.
\asubsection{Honorary and Advisory Membership Term}
Honorary and Advisory Memberships shall last until the member resigns.

@@

\asubsection{Responsibilities of the Social Director(s)}
\begin{enumerate}
	\item To preside over Social Meetings in which House members are encouraged to bring ideas for social events
	\item To exercise general supervision over Social operations
	\item To oversee the organization, initiation, and execution of House social activities
  \item To ensure that there is a variety of events for House members to participate in throughout the academic year
\end{enumerate}

@@

\asubsubsection{Expenditure Approval}
All House expenditures must be approved by the Financial Director and the Director whose budget is going to be used for the expenditure.
Single expenditures may not exceed seventy-five dollars (\$75) and total expenditures (funds drawn for a specific event, project, piece of equipment, or service) may not exceed one-hundred dollars (\$100).
\\* \\*
If the above amounts are to be exceeded, the expenditure must be approved by a Simple Majority vote at House meeting before the funds may be appropriated, as defined in \ref{Simple Majority}.
At the Financial Director's discretion, a Spending Committee may be held in order to approve any purchase exceeding one-hundred dollars (\$100), but not exceeding three-hundred dollars (\$300).
A quorum of one-quarter the number of current active members is required for the meeting to take place and for any vote to be considered valid, it must be passed by a simple two-thirds majority.
\\*\\*
For expenditures exceeding \$300 in total funding, a Spending Presentation must be presented to House at a House meeting.
This presentation includes the funds required for the expenditure, inventory of required resources, and (if applicable) a timeline for completion.
\\* \\*
If an appropriate Directorship cannot be determined for an expenditure, it is to be brought up for approval at House meeting as a Miscellaneous expenditure and approved by a simple majority vote, regardless of the amount.
This amount is to be directly subtracted from the general CSH account.
\\* \\*
Funds allocated for a project not spent by the end of the Standard Operating Session \ref{Standard Operating Session} in which they were approved are voided, unless otherwise specified during the original voting process.

@@

\asubsubsubsection{The Evaluation Period}
The Process will occur either once or twice per semester, and will last for six (6) weeks.
The Process shall be initiated by the Evals Director during either the first and second week of each semester.
E-Board may hold a closed ballot Simple Majority vote to extend the Intro Process or the Intro Packet.
If an Intro Process is extended, the Introductory Evaluation shall occur at the termination of the extended Process, which may be outside of the period defined in \ref{Introductory Evaluation}.
If deemed necessary by the Evals Director, or by an E-Board simple majority vote, the second intro process must begin within nine (9) days of the first process ending.
If a second Intro Process is approved, the Evals Director may initiate a new Intro Packet within the first or second week of the Intro Process.

\asubsubsubsection{The Introductory Packet}

Each Intro Process participant, after the first week, is given two (2) weeks to obtain signatures from all Active Members who have passed a Membership Evaluation, all On-Floor Intro Members, and ten (10) of any combination of the following:
\begin{itemize}
	\item Alumni members
	\item Honorary members
	\item Advisory members
\end{itemize}
At the discretion of the Evals Director, any Intro Packet may be extended to accommodate extenuating circumstances.

@@

\asubsubsubsection{Introductory Evaluation}

The Introductory Evaluation is the process by which House chooses which Intro Members to extend an offer of Active Membership.
It occurs at the conclusion of the final week of the Process.

\asubsubsubsubsection{Voting}

On a member by member basis, this evaluation process determines if each Intro Member has successfully completed the Intro Process requirements \ref{Expectations of an Introductory Member}.
A Simple Majority vote with a quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
In order for an Active Member to be counted as a Possible Vote they must meet the requirements outlined in \ref{Expectations of Voting Members}.
Neither absentee nor proxy votes are allowed.
House may choose any of the Outcomes for each member.

\asubsubsubsubsection{Expectations of Voting Members}

The following requirements must be met by the beginning of the Introductory Evals for an Active Member to be allowed to vote. 
Any of these requirements may be waived by the Evals Director or a simple majority vote by E-Board
\begin{itemize}
\item Attend all House meetings during the process
\item Attend at least one House directorship meeting for each week of the process (including permanent and Ad Hoc directorship meetings)
\item Attend at least one House social event during the process
\item Attend at least two seminars relating to computing or electronics
\end{itemize}

\asubsubsubsubsection{Outcomes}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}

	\item Intro Members may be offered Active Membership (\ref{Active Membership}) provided they meet the requirements described in \ref{Expectations of an Introductory Member}, at the discretion of House.
	\item If an Intro Member fails to meet the requirements, their membership will be revoked.
	\item An Intro member may be given a conditional to complete as a means of making up for missing requirements.
		A conditional may be proposed by any member present at the Introductory Evaluation and, if it is approved by the Evals Director, is then voted on by House.
		Each conditional consists of a set of additional requirements and a deadline for completing them.
		When the deadline expires, the conditional will be brought before E-Board who will assess its completeness.
		A conditional member who does not meet these additional requirements forfeits membership.
\end{enumerate}

@@

% Current RIT students is defined as students who have attended RIT for at least 1 full semester
\asubsubsubsection{Selection Process for Current RIT Students}
\begin{enumerate}
	\item The applicant submits an application to the Evals Director for review.
	\item The applicant participates in an informal interview with exactly three current Active, Alumni, or Honorary Members.
	\item The application materials are then reviewed at an Evals meeting.
	Then a simple majority vote, of attending members, is held on whether or not to accept the person as an Intro Member.
\end{enumerate}
Note: Most membership privileges do not initiate until successful completion of the Intro Process.
This means that until the member has passed the Introductory Evals, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
The member does, however, have the right to use Computer Science House's facilities.
The member is not required to pay dues during the Intro Process.
\\* \\*
Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.

% Incoming RIT students is defined as students who have attended RIT for less than 1 full semester
\asubsubsubsection{Selection Process for Incoming RIT Students}
\begin{enumerate}
	\item During Spring semester, the Evals Director selects a group of Active Members to form a Selections Committee.
		The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by ResLife.
        \item A subset of applicants will be offered Introductory Membership and must participate in the Intro Process defined in \ref{The Introductory Process}. 
            A subset of Intro Members will be offered On-Floor status and will be able to select a room on floor. 
            The other Intro Members will have Off-Floor status, but will otherwise have the same privileges and responsibilities.
\end{enumerate}
Note: Most membership privileges do not initiate until successful completion of the Intro Process.
This means that until the member has passed the Introductory Evals, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
The member does, however, have the right to use Computer Science House's facilities.
The member is not required to pay dues during the Intro Process.
\\* \\*
Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.

\asubsubsubsection{Selection Process for Honorary Members}
\begin{enumerate}
	\item A House Member submits to the Evals Director a nomination for a person they feel is deserving of Honorary Membership.
	\item The Evals Director performs some preliminary research on the candidate and presents the findings.
	\item E-Board decides whether or not to present the nomination to the House for a secret ballot House vote.
		If E-Board decides not to present the nomination to the House, the Selection Process ends and the candidate does not become an Honorary Member.
	\item The nomination is presented at a House Meeting for discussion and a Two-Thirds vote, as described in \ref{Two-Thirds}.
		Ballots are distributed and voting must remain open for a minimum of forty-eight hour period.
	\item The candidate is notified of their selection as an Honorary Member and presented with the honor.
\end{enumerate}

\asubsubsubsection{Selection Process for Advisory Members}
\begin{enumerate}
	\item When there is a perceived need, E-Board may open nominations for Advisory Members.
		After an announcement at House Meeting, during a 72-hour period, any House Member may submit a nomination.
	\item After the close of the nomination collection period, E-Board will arrange some means for the House to meet with the nominees.
	\item A discussion of the candidates will be held at the following House meeting.
	\item Ballots are distributed for each nominee as a fifty-percent House vote defined in \ref{Fifty Percent}.
		Voting must remain open for a minimum of a forty-eight hour period.
	\item All candidates selected are notified of their acceptance as House Advisors and asked to accept or decline the selection.
\end{enumerate}

@@

\asubsubsubsubsection{Voting}
Any Active Member who has completed all of the requirements as defined in \ref{Expectations of House Members} at the beginning of the Membership Evals passes their Membership Evals without being voted on or evaluated by the quorum.
All Active Members who have not recieved an exemption from E-Board prior to the Membership Evals will be evaluated on a Member by Member basis by a quorum of Active Members.
The Membership Evals shall hold members to the objective requirements defined in \ref{Expectations of House Members} and determine which members may continue as an Active Member in the following Standard Operating Session.
Exceptions to the requirements may be made, as House may choose any of the Outcomes for each Member, even if the Member being evaluated has not completed all of their requirements.
These requirements must be completed before the Membership Evals occurs.
A Secret Immediate Simple Majority vote with a Quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
Neither absentee nor proxy votes are allowed.

\asubsubsubsubsection{Outcomes}
Members who pass Membership Evals have the option to participate as an Active Member in the following year and remain on the upcoming roster if applicable.
\\* \\*
If a member fails and has never passed a Membership Evals in the past, their membership will be revoked immediately.
If the member has previously passed a Membership Evals they will move to Alumni Membership status at the end of the Standard Operating Session (\ref{Alumni Membership Selection}).
In either case, the member forfeits their ability to be included on the following year’s roster.
\\* \\*
A member may be given a conditional to complete as a means of making up for missing requirements.
A conditional may be proposed by any member present at the Evaluation.
If the conditional is approved by the Evals Director, it is then voted on by House.
Each conditional consists of a set of additional requirements a deadline for completing them.
When the deadline expires, the conditional will be brought before E-Board who will assess its completeness.
A conditional member who does not meet these additional requirements will have failed the evaluation.

@@

\asubsubsection{Housing Status}
All Alumni, Active, and Intro Members have a housing status.
This status indicates their right to priority housing on the floor.
Alumni Members in good standing keep the housing status they had as Active Members.
Alumni Members in bad standing have Off-Floor status.

\asubsubsubsection{On-Floor Status}
Members with On-Floor status are eligible to live on the floor.
To be granted On-Floor status, members may notify the Evals Director that they would like to come up for a vote.
The Evals Director will then bring them up for vote at the next meeting.

@@

\asubsection{Operations of the OpComm Directorship}
The OpComm Directorship is responsible for overseeing the implementation of maintenance and upgrades to the House Computer Systems Network.
It is a self-governing committee making decisions by a simple majority vote.
Membership is composed of all RTPs.

\asubsubsection{Selection of an RTP}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Nominations are taken from the RTPs and Prior RTPs meeting the selection criteria in \ref{Qualifications of an RTP}.
	\item Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
	\item A list of all nominees who have accepted is presented to E-Board for approval.
		This E-Board Meeting is closed to E-Board Members, RTPs, and House members with explicit invitation from the E-Board.
	\item If an E-Board member is a candidate for the office in discussion, the member is absent and their vote is abstained.
		A simple majority E-Board vote, as described in \ref{Simple Majority}, is taken to determine whether the nominations of the RTPs are accepted.
\end{enumerate}

@@

\asubsubsubsection{Changes}
The following process is used for making changes to the Code of Conduct document.
\begin{enumerate}
	\item An RTP drafts a change to the Code of Conduct and makes publicly available both the summary and difference file of the change.
	\item The change is proposed at a House Meeting and is discussed at the same House Meeting.
	\item The final proposal is presented at the next House Meeting and ballots are distributed for a Balloted House vote as described in \ref{Balloted Vote}.
\end{enumerate}

@@

\asubsection{Waiving of Qualifications}
\begin{enumerate}
  \item House may choose to waive the following subset of the Qualifications for E-Board positions (defined under \ref{Qualifications}) for all Candidates:
    \begin{enumerate}
      \item Candidates must reside on floor during the term of office.
      \item Candidates must have at least one full semester of House membership as an Active Member.
      \item Social and R\&D are the only voting E-Board positions that allow for Dual Directorship.
    \end{enumerate}
  \item When a waiver is proposed, the Chair of the Vote shall state which E-Board position and Qualification is being voted upon, and any nominated Candidates not qualified under \ref{Qualifications} who would become qualified if the waiver passes.
  \item A Three-Quarters Immediate Vote, as defined in \ref{Three-Quarters} and \ref{Immediate Vote}, is then taken to determine whether the proposed waiver shall take effect.
  \item Each vote to waive a Qualification must only apply to a single Qualification for a single E-Board position.
  \item Waivers always apply to all Candidates for the E-Board position.
\end{enumerate}

>>>>

\asubsection{Non-Semantic Changes}
There are two methods for non-semantic change to the Constitution.
A Maintainer may approve any proposed change that does not affect the meaning of the document.
Alternatively, the change may be presented to the House for discussion followed by an Immediate One-Half Vote with fifty percent Quorum.

\asubsection{Semantic Changes}
Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in the House during the week.
The final proposal is presented the following week and ballots are distributed for a Balloted Two-Thirds Vote with Two-Thirds Quorum \ref{Balloted Vote}.
The ballots are collected for a minimum of a forty-eight hour period.
The Constitution may be overridden by an Nine-Tenths Immediate Vote with eighty-five percent Quorum.

@@

\asubsection{Maintainer Expectations}
Maintainers are expected to:
\begin{itemize}
	\item Be knowledgeable about the Constitution
	\item Review changes to the Constitution for grammar, spelling, and internal consistency
	\item Participate in discussion of proposals and amendments
	\item Keep a public record of changes to the Constitution
\end{itemize}

Failure to meet any of these expectations is grounds for revocation of Maintainer status by E-Board.

\asubsection{Maintainer Term}
Maintainer status lasts until it is resigned, or until it is revoked by an E-Board Vote.
If a Maintainer no longer satisfies \ref{Maintainer Qualifications}, they lose Maintainer status.

\asubsection{Maintainer Selection}
Any member may nominate a qualified member for Maintainer status to E-Board for consideration.
E-Board may choose to approve or reject the nomination by an E-Board Vote.

@@

\asubsection{Active Membership Selection}

Alumni Members in good standing may self-select into Active Membership by paying dues to the Financial Director and notifying the Evaluations Director. They will retain their previous Housing Status if applicable.
\\*\\*
Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate.
The Evals Director will then bring them up for an Immediate Relative Majority vote with fifty percent Quorum at the next House meeting.

If the vote passes the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.

@@

\asubsection{Active Membership Privileges}
Active Members receive the privilege to:
\begin{itemize}
	\item Vote on all issues brought before the House
	\item Reside on the House
	\item Hold an E-Board office on the House
	\item Use Computer Science House facilities
	\item Attend Computer Science House functions
	\item Receive priority for available housing on the House when returning from cooperative education
	\item Guaranteed housing in compliance with ResLife policies regarding Special Interest Houses and the Housing Selection Process (if they have On-Floor status)
\end{itemize}

@@

\asection{Honorary and Advisory Memberships}
\asubsection{Honorary Membership Qualifications}
Honorary Membership is open to a person whom the House feels has contributed great personal effort to the House and is deserving of House recognition.
\asubsection{Advisory Membership Qualifications}
Advisory Membership is open to all members of the Rochester Institute of Technology professional, academic, or administrative staff.
\asubsection{Honorary and Advisory Membership Selection}
\begin{enumerate}
	\item A House Member submits to the Evals Director a nomination, in writing, for a person they feel is deserving of Honorary or Advisory Membership. The nomination must specify the type of membership the nominee is nominated for.
	\item The Evals Director performs preliminary research on the candidate and presents the findings.
	\item E-Board decides whether or not to present the nomination to the House for a secret ballot House vote.
		If E-Board decides not to present the nomination to the House, the Selection Process ends and the candidate does not become a Member.

	\item The nomination is presented at a House Meeting for discussion and a Two-Thirds vote, as defined in \ref{Two-Thirds}.
		Ballots are distributed and voting must remain open for a minimum of forty-eight hour period.
	\item Candidates selected for Honorary Membership are notified of their selection as an Honorary Member and presented with the honor.
    \item Candidates selected for Advisory Membership are notified of their acceptance as House Advisors and asked to accept or decline
        the selection.
\end{enumerate}
\asubsection{Honorary Membership Expectations}
Honorary Members are encouraged to remain in contact with the House.
\asubsection{Advisory Membership Expectations}
Advisors are encouraged to offer advice and assistance to the House in any capacity the Advisor is able to help.
Advisors are also encouraged to meet House members and occasionally attend House activities.
\asubsection{Honorary and Advisory Membership Privileges}
Honorary and Advisory Members may advise in all issues brought before the House, use Computer Science House facilities, and attend Computer Science House functions.
\asubsection{Honorary and Advisory Membership Evaluations}
Honorary and Advisory Members are not subject to formal evaluations.
\asubsection{Honorary and Advisory Membership Resignations}

An Honorary or Advisory Member may resign by submitting in writing the reason for resignation to the Chair.
The resignation will be read at the following House Meeting and become effective at that time.
\asubsection{Honorary and Advisory Membership Term}
Honorary and Advisory Memberships shall last until the member resigns.

@@

\asubsection{Responsibilities of the Social Director(s)}
\begin{enumerate}
	\item To preside over Social Meetings in which House members are encouraged to bring ideas for social events
	\item To exercise general supervision over Social operations
	\item To oversee the organization, initiation, and execution of House social activities
  \item To ensure that there is a variety of events for House members to participate in throughout the academic year
  \item To vote on issues presented to the Executive Board
\end{enumerate}

@@

\asubsubsection{Expenditure Approval}
All House expenditures must be approved by the Financial Director and the Director whose budget is going to be used for the expenditure.
Single expenditures may not exceed seventy-five dollars (\$75) and total expenditures (funds drawn for a specific event, project, piece of equipment, or service) may not exceed one-hundred dollars (\$100).
\\* \\*
If the above amounts are to be exceeded, the expenditure must be approved by an Immediate Relative Majority Vote at a House meeting before the funds may be appropriated.
At the Financial Director's discretion, a Spending Committee meeting may be held in order to approve any purchase exceeding one-hundred dollars (\$100), but not to exceed three-hundred dollars (\$300).
A Two-Thirds Immediate Vote with twenty-five percent Quorum is required to approve the purchase.
\\*\\*
For expenditures exceeding \$300 in total funding, a Spending Presentation must be presented to House at a House meeting.
This presentation includes the funds required for the expenditure, inventory of required resources, and (if applicable) a timeline for completion.
\\* \\*
If an appropriate Directorship cannot be determined for an expenditure, it is to be brought up for approval at House meeting as a Miscellaneous expenditure and approved by an Immediate Relative Majority vote with fifty percent Quorum, regardless of the amount.
This amount is to be directly subtracted from the general CSH account.
\\* \\*
Funds allocated for a project not spent by the end of the Standard Operating Session \ref{Standard Operating Session} in which they were approved are voided, unless otherwise specified during the original voting process.

@@

\asubsubsubsection{The Evaluation Period}
The Process will occur either once or twice per semester, and will last for six (6) weeks.
The Process shall be initiated by the Evaluations Director during either the first and second week of each semester.
The Executive Board may approve an extension to the Introductory Process by an Executive Board Vote.
If an Introductory Process is extended, the Introductory Evaluation shall occur at the termination of the extended Process, which may be outside of the period defined in \ref{Introductory Evaluation}.
If deemed necessary by the Evaluations Director, or by an Executive Board Vote, the second intro process must begin within nine (9) days of the first process ending.
If a second Introductory Process is approved, the Evaluations Director may initiate a new Introductory Packet within the first or second week of the Introductory Process.
\asubsubsubsection{The Introductory Packet}
Each Introductory Process participant, after the first week, is given two (2) weeks to obtain signatures from all Active Members who have passed a Membership Evaluation, all On-Floor Introductory Members, and ten (10) of any combination of the following:

\begin{itemize}
	\item Alumni members
	\item Honorary members
	\item Advisory members
\end{itemize}
At the discretion of the Evals Director or an E-Board Vote, any Intro Packet may be extended to accommodate extenuating circumstances.

@@

\asubsubsubsection{Introductory Evaluation}
The Introductory Evaluation is the process by which House chooses which Introductory Members to extend an offer of Active Membership.
It occurs at the conclusion of the final week of the Process.

\asubsubsubsubsection{Voting}
On a member by member basis, this evaluation process determines if each Introductory member has successfully completed the Introductory Process requirements \ref{Expectations of an Introductory Member}.
An Immediate Relative Majority Vote with two-thirds Quorum is required for the evaluation to be valid.
For an Active Member to be eligible to vote during the evaluation process they must meet the requirements outlined in \ref{Expectations of Voting Members}.

Neither absentee nor proxy votes are allowed.
House may choose any of the Outcomes for each member.

\asubsubsubsubsection{Expectations of Voting Members}
The following requirements must be met by the beginning of the Introductory Evaluation for an Active Member to be allowed to vote. 
Any of these requirements may be waived by the Evals Director or an E-Board Vote.

\begin{itemize}
\item Attend all House meetings during the process
\item Attend at least one House directorship meeting for each week of the process (including permanent and Ad Hoc directorship meetings)
\item Attend at least one House social event during the process
\item Attend at least two seminars relating to computing or electronics
\end{itemize}

\asubsubsubsubsection{Outcomes}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Introductory Members may be offered Active Membership (\ref{Active Membership}) provided they meet the requirements described in \ref{Expectations of an Introductory Member}, at the discretion of House.
	\item If an Introductory Member fails to meet the requirements, their membership will be revoked.
	\item An Introductory member may be given a conditional to complete as a means of making up for missing requirements.
		A conditional may be proposed by any member present at the Introductory Evaluation and, if it is approved by the Evaluations Director, is then voted on by House.
		Each conditional consists of a set of additional requirements and a deadline for completing them.
		When the deadline expires, the conditional will be brought before E-Board who will assess its completeness.
		A conditional member who does not meet these additional requirements forfeits membership.
\end{enumerate}

@@

% Current RIT students is defined as students who have attended RIT for at least 1 full semester
\asubsubsubsection{Selection Process for Current RIT Students}
\begin{enumerate}
	\item The applicant submits an application to the Evals Director for review.
	\item The applicant participates in an informal interview with exactly three current Active, Alumni, or Honorary Members.
	\item The application materials are then reviewed at an Evals meeting.
	Then an Immediate Relative Majority Vote of attending members is held on whether or not to accept the person as an Intro Member.
\end{enumerate}
Note: Most membership privileges do not initiate until successful completion of the Intro Process.
This means that until the member has passed the Introductory Evals, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
The member does, however, have the right to use Computer Science House's facilities.
The member is not required to pay dues during the Intro Process.
\\* \\*
Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.

% Incoming RIT students is defined as students who have attended RIT for less than 1 full semester
\asubsubsubsection{Selection Process for Incoming RIT Students}
\begin{enumerate}
	\item During Spring semester, the Evaluations Director selects a group of Active Members to form a Selections Committee.
		The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by Residence Life.
        \item A subset of applicants will be offered Introductory Membership and must participate in the Introductory Process defined in \ref{The Introductory Process}. 
            A subset of Introductory Members will be offered On-Floor status and will be able to select a room on floor. 
            The other Introductory Members will have Off-Floor status, but will otherwise have the same privileges and responsibilities.
\end{enumerate}
Note: Most membership privileges do not initiate until successful completion of the Intro Process.
This means that until the member has passed the Introductory Evals, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
The member does, however, have the right to use Computer Science House's facilities.
The member is not required to pay dues during the Intro Process.
\\* \\*
Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.

\asubsubsubsection{Selection Process for Honorary Members}
\begin{enumerate}
	\item A House Member submits to the Evaluations Director a nomination for a person they feel is deserving of Honorary Membership.
	\item The Evaluations Director performs some preliminary research on the candidate and presents the findings.
	\item The Executive Board decides whether or not to present the nomination to the House for a secret ballot House vote.
		If the Executive Board decides not to present the nomination to the House, the Selection Process ends and the candidate does not become an Honorary Member.
	\item The nomination is presented at a House Meeting for discussion and a Two-Thirds Balloted Vote with two-thirds Quorum.
		Ballots are distributed and voting must remain open for a minimum of forty-eight hour period.
	\item The candidate is notified of their selection as an Honorary Member and presented with the honor.
\end{enumerate}

\asubsubsubsection{Selection Process for Advisory Members}
\begin{enumerate}
	\item When there is a perceived need, E-Board may open nominations for Advisory Members.
		After an announcement at House Meeting, during a 72-hour period, any House Member may submit a nomination.
	\item After the close of the nomination collection period, E-Board will arrange some means for the House to meet with the nominees.
	\item A discussion of the candidates will be held at the following House meeting.
	\item Ballots are distributed for each nominee as a One-Half Balloted Vote with fifty percent Quorum.
		Voting must remain open for a minimum of a forty-eight hour period.
	\item All candidates selected are notified of their acceptance as House Advisors and asked to accept or decline the selection.
\end{enumerate}

@@

\asubsubsubsubsection{Voting}
Any Active Member who has completed all of the requirements as defined in \ref{Expectations of House Members} at the beginning of the Membership Evals passes their Membership Evals without being voted on or evaluated by the quorum.
All Active Members who have not recieved an exemption from E-Board prior to the Membership Evals will be evaluated on a Member by Member basis by a quorum of Active Members.
The Membership Evals shall hold members to the objective requirements defined in \ref{Expectations of House Members} and determine which members may continue as an Active Member in the following Standard Operating Session.
Exceptions to the requirements may be made, as House may choose any of the Outcomes for each Member, even if the Member being evaluated has not completed all of their requirements.
These requirements must be completed before the Membership Evaluation occurs.
A Secret Immediate Relative Majority vote with two-thirds Quorum is required for the evaluation to be valid.
Neither absentee nor proxy votes are allowed.

\asubsubsubsubsection{Outcomes}
Members who pass Membership Evals have the option to participate as an Active Member in the following year and remain on the upcoming roster if applicable.
\\* \\*
If a member fails and has never passed a Membership Evals in the past, their membership will be revoked immediately.
If the member has previously passed a Membership Evals they will move to Alumni Membership status at the end of the Standard Operating Session (\ref{Alumni Membership Selection}).
In either case, the member forfeits their ability to be included on the following year’s roster.
\\* \\*
A member may be given a conditional to complete as a means of making up for missing requirements.
A conditional may be proposed by any member present at the Evaluation.
If the conditional is approved by the Evaluations Director, it is then voted on by House as described in \ref{Voting}.
Each conditional consists of a set of additional requirements a deadline for completing them.
When the deadline expires, the conditional will be brought before E-Board who will assess its completeness.
A conditional member who does not meet these additional requirements will have failed the evaluation.

@@

\asubsubsection{Housing Status}
All Alumni, Active, and Introductory Members have a housing status.
This status indicates their right to priority housing on the floor.
Alumni Members in good standing keep the housing status they had as Active Members.
Alumni Members in bad standing have Off-Floor status.

\asubsubsubsection{On-Floor Status}
Members with On-Floor status are eligible to live on the floor.
To be granted On-Floor status, members may notify the Evaluations Director that they would like to come up for a vote.
The Evaluations Director will then bring them up for a One-Half Immediate vote among attending Active members at the next evaluations meeting.
If the Evaluations Director determines that too few members are present to hold a vote, the member will be brought up for a vote at the next evaluations meeting.

@@

\asubsection{Operations of the Operational Communications Directorship}
The Operational Communications Directorship is responsible for overseeing the implementation of maintenance and upgrades to the House Computer Systems Network.
It is a self-governing committee making decisions by Immediate Relative Majority vote (two-thirds Quorum) of Current Root Type Persons.
Membership is composed of all Root Type Persons.

\asubsubsection{Selection of an RTP}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Nominations are taken from the RTPs and Prior RTPs meeting the selection criteria in \ref{Qualifications of an RTP}.
	\item Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
	\item A list of all nominees who have accepted is presented to the Executive Board for approval.
		This Executive Board Meeting is closed to the Executive Board Members, Root Type Persons, and House members with explicit invitation from the Executive Board.
	\item If an Executive Board member is a candidate for the office in discussion, the member is absent and their vote is abstained.
		An Executive Board Vote is taken to determine whether the nominations of the Root Type Persons are accepted.
\end{enumerate}

@@

\asubsubsubsection{Changes}
The following process is used for making changes to the Code of Conduct document.
\begin{enumerate}
	\item An RTP drafts a change to the Code of Conduct and makes publicly available both the summary and difference file of the change.
	\item The change is proposed at a House Meeting and is discussed at the same House Meeting.
	\item The final proposal is presented at the next House Meeting and ballots are distributed for a One-Half Balloted House vote (fifty percent Quorum) as described in \ref{Balloted Vote}.
\end{enumerate}

@@

\asubsection{Waiving of Qualifications}
\begin{enumerate}
  \item House may choose to waive the following subset of the Qualifications for E-Board positions (defined under \ref{Qualifications}) for all Candidates:
    \begin{enumerate}
      \item Candidates must reside on floor during the term of office.
      \item Candidates must have at least one full semester of House membership as an Active Member.
      \item Social and R\&D are the only voting E-Board positions that allow for Dual Directorship.
    \end{enumerate}
  \item When a waiver is proposed, the Chair of the Vote shall state which Executive Board position and Qualification is being voted upon, and any nominated Candidates not qualified under \ref{Qualifications} who would become qualified if the waiver passes.
  \item A Three-Quarters Immediate Vote with three-quarters Quorum is then taken to determine whether the proposed waiver shall take effect.
  \item Each vote to waive a Qualification must only apply to a single Qualification for a single Executive Board position.
  \item Waivers always apply to all Candidates for the Executive Board position.
\end{enumerate}
